A Three-Step Approach for Assessing Landscape Connectivity via Simulated Dispersal: African Wild Dog Case Study

### 2024-07-01 Chapter_1/04_Manuscript/Manuscript.tex
Publish PHD

\noindent The probability of a step \(i\) being realized was then contingent on
the step's selection score, as well as on the selection scores of all other step
in the same stratum:

>>>>

\noindent The probability of a step \(i\) being realized was then contingent on
the step's selection score, as well as on the selection scores of all other
steps in the same stratum:
